Developing a preprint culture in biology

### 2013-01-26 ms.tex
fix figure

In contrast to other disciplines, the field of biology has effectively no
preprint culture, with the exception of small pockets of primarily highly
quantitative research (\emph{e.g.}, epidemiology, population genetics).  While
submitting to preprint servers has become more common in the past few years, the
number of biology papers submitted to preprint servers still represents only a
small fraction of the total research produced in biology (Fig.~\ref{arxiv}).

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4in]{figure_2.png}
\end{center}
\caption { Submissions to the quantitative biology section lag behind
physics, mathematics, and computer science.
}
\label{fig:arxiv}
\end{figure}

>>>>

In contrast to other disciplines, the field of biology has effectively no
preprint culture, with the exception of small pockets of primarily highly
quantitative research (\emph{e.g.}, epidemiology, population genetics).  While
submitting to preprint servers has become more common in the past few years, the
number of biology papers submitted to preprint servers still represents only a
small fraction of the total research produced in biology (Fig.~\ref{fig:arxiv}).

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics[width=4in]{figure_2.eps}
\end{center}
\caption { Submissions to the quantitative biology section lag behind
physics, mathematics, and computer science.
}
\label{fig:arxiv}
\end{figure}
